---
title: "No Title Yet"
author: "Yukai Yang"
output:
  word_document: default
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(flextable)
require(Matching)
require(sandwich)
# load the data
dat = read.table("data230125.dat")
```

## The Framework of the Causal Effect Analysis


```{r makedatm, echo=F}
source("experiments/datmanip.R")
flextable(tab) %>%  merge_v() %>% autofit() %>%
  set_caption(caption = "Variables and descriptions in the analysis")
```


## Results

The analysis of the situation at the three months follow-up. We remove the patients who retired or deceased at 3 month.

```{r exp0, include=F}
source("experiments/exp0.R")
```

```{r res0, echo=F}
tab
```

```{r exp1, include=F}
source("experiments/exp1.R")
```

```{r res1, echo=F}
#round(tab,4) %>% kbl(align="c") %>% kable_styling(bootstrap_options = c("striped", "hover"))
tab
```

```{r exp2, include=F}
source("experiments/exp2.R")
```

```{r res2, echo=F}
#round(tab,4) %>% kbl(align="c") %>% kable_styling(bootstrap_options = c("striped", "hover"))
tab
```

```{r exp3, include=F}
source("experiments/exp3.R")
```

```{r res3, echo=F}
#round(tab,4) %>% kbl(align="c") %>% kable_styling(bootstrap_options = c("striped", "hover"))
tab
```




## References

Holland P.W. (1986). "Statistics and Causal Inference." Journal of the American Statistical
Association, 81(396), 945–960.

Splawa-Neyman J. (1923). "On the Application of Probability Theory to Agricultural Experiments. Essay on Principles. Section 9." Statistical Science, 5(4), 465–472. Trans. Dorota M. Dabrowska and Terence P. Speed.

Rubin D.B. (1974). "Estimating Causal Effects of Treatments in Randomized and Nonrandomized Studies." Journal of Educational Psychology, 66, 688–701.

Rubin D.B. (1978). "Bayesian Inference for Causal Effects: The Role of Randomization." The Annals of Statistics, 6(1), 34–58.

Rubin D.B. (1990). "Comment: Neyman (1923) and Causal Inference in Experiments and Observational Studies." Statistical Science, 5(4), 472–480.

Rosenbaum P.R., Rubin D.B. (1983). "The Central Role of the Propensity Score in Observational
Studies for Causal Effects." Biometrika, 70(1), 41–55.
